---
title: "infer 02 - Numerical inference"
author: "Daniel Jiménez"
date: "12/19/2019"
output: html_document
---



```{r}
library(infer);
library(tidyverse);
library(emo);
theme_set(theme_classic())

```



# Some approach
## Bootstrapping techniques

* First : Bootstrap is a powerful method for statistical inference (with based on computational algorithms) that allows assigning measures of accuracy to sample estimates.

* Second : It`s widely applied in other statistical inference such as 
    + Confidence interval
    + Regression Models
    + Machine Learning
    
Some conceptions : i) Assume the data is representative, ii) use random sample with replacement to make inferences about the unknown population (statistical universe). iii) Calculate or compute robust statistics tools - mean, variance , error , median , etc through on samples. iv) repeat steps many times to creat bootstrap distribution


In this example , with iris `emo::ji("face")` I generate bootstrap distribution for median. 



```{r}
sepal_med_ci<-iris%>%
  specify(response = Sepal.Length )%>% # Specify the variable of interes
  generate(reps = 100, type="bootstrap")%>%
  calculate(stat = "median")

sepal_med_ci%>%
  head()%>%
  knitr::kable(format = 'markdown', caption = 'Bootstrap Distribution for media')
```




Now , is necessary generate histogram plot about this

```{r}
sepal_med_ci%>%
  ggplot(aes(stat))+
  geom_histogram(bins = 10)+
  labs(title = 'Boostrap Distribution')+
  theme(plot.title = element_text(hjust = 0.5))
```


##





## References 
* https://towardsdatascience.com/an-introduction-to-the-bootstrap-method-58bcb51b4d60

*  

![](https://www.youtube.com/watch?v=O_Fj4q8lgmc)



